\propertitle

### 2020-02-03 maxNt_v6.tex
update

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-01-24T12:54:04+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{4 November 2015}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, E. Torre, V. Rostami}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Paper's details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\propertitle}
\author{%
\hspace*{\stretch{1}}%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering P.G.L.  Porta Mana\\%
\footnotesize\epost{\email{pgl}{portamana.org}}}%
\hspace*{\stretch{1}}%
%% uncomment if additional authors present
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering E. Torre\\%
\footnotesize\epost{\email{torre}{ibk.baug.ethz.ch}}}%
\hspace*{\stretch{1}}\\%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering V. Rostami\\%
\footnotesize\epost{\email{vrostami}{uni-koeln.de}}}%
\hspace*{\stretch{1}}%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering Y. Roudi\\%
\footnotesize\epost{\email{yasser.roudi}{ntnu.no}}}%
\hspace*{\stretch{1}}%
%\quad\href{https://orcid.org/0000-0002-6070-0784}{\protect\includegraphics[scale=0.16]{orcid_32x32.png}\textsc{orcid}:0000-0002-6070-0784}%
}

@@

The question of how large the larger population addressed by model should
or can be, and the assumptions on which the model is based, from a Bayesian
point of view, are also discussed. \\\noindent\emph{\footnotesize Note:
  Dear Reader \amp\ Peer, this manuscript is being peer-reviewed by you.
  Thank you.}
% \par%\\[\jot]
% \noindent
% {\footnotesize PACS: ***}\qquad%
% {\footnotesize MSC: ***}%
%\qquad{\footnotesize Keywords: ***}
\end{abstract}
\selectlanguage{british}\frenchspacing

@@

The two infinity approximations are at the boundary of their validity in
our examples. For this reason we interpret the maximum-entropy distribution
as the \emph{most probable frequency distributions}, as mentioned at the
end of \sect~\ref{sec:model}. An important question, then, is \emph{which
  features of the maximum-entropy frequency distribution are typical of the
  majority of plausible frequency distributions?} Especially for features
such as number, position, height of modes, or tail behaviour. Preliminary
studies using a full probability calculation (to be published separately)
show that several semi-quantitative features of the maximum-entropy
distribution are indeed typical. For the first data set, for example, most
frequency distributions have two high-frequency regimes of activity, as in
\fig~\ref{fig:plots_5mom_a}, with roughly the same heights and almost the
same locations, within a few percentages of population-averaged activity.
Each of the two high-frequency regimes, though, may consist of two or three
very close modes rather than one. The same preliminary studies also
indicate that these typical features are insensitive to alternative prior choices
in the second assumption above, for example using a Dirichlet prior instead
of an entropic one.

@@

Some approximations implicit in the model make its numerical results
semi-quantitative with respect to an exact analysis. The results should not
be off by more than a few percentages for the population-averaged activity and
for the frequency density. This imprecision, however, is compensated by the
extreme computational cheapness of the model, far less costly than an exact
analysis. The model is therefore very convenient at least for essaying
hypotheses. We hope to present an exact quantitative comparison with the
full probabilistic approach in a future publication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\defbibnote{prenote}{{\footnotesize (\enquote{de $X$} is listed under D,
    \enquote{van $X$} under V, and so on, regardless of national
    conventions.)\par}}
% \defbibnote{postnote}{\par\medskip\noindent{\footnotesize% Note:
%     \arxivp \mparcp \philscip \biorxivp}}

>>>>

\pdfoutput=1
%% Author: PGL  Porta Mana
%% Created: 2015-05-01T20:53:34+0200
%% Last-Updated: 2020-02-03T11:24:40+0100
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newif\ifarxiv
\arxivfalse
\ifarxiv\pdfmapfile{+classico.map}\fi
\newif\ifafour
\afourfalse% true = A4, false = A5
\newif\iftypodisclaim % typographical disclaim on the side
\typodisclaimtrue
\newcommand*{\memfontfamily}{zplx}
\newcommand*{\memfontpack}{newpxtext}
\documentclass[\ifafour a4paper,12pt,\else a5paper,10pt,\fi%extrafontsizes,%
onecolumn,oneside,article,%french,italian,german,swedish,latin,
british%
]{memoir}
\newcommand*{\updated}{\today}
\newcommand*{\firstdraft}{4 November 2015}
\newcommand*{\firstpublished}{4 November 2015}
\newcommand*{\propertitle}{Inferring the total activity of a large neuronal population\\ from a small sample}
\newcommand*{\pdftitle}{\propertitle}
\newcommand*{\headtitle}{Inferences about large neuronal populations}
\newcommand*{\pdfauthor}{P.G.L.  Porta Mana, Y. Roudi, E. Torre, V. Rostami}
\newcommand*{\headauthor}{Porta Mana \etal}
\newcommand*{\reporthead}{}% Report number

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Paper's details
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\title{\propertitle}
\author{%
\hspace*{\stretch{1}}%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering P.G.L.  Porta Mana\\%
\footnotesize\epost{\email{piero.mana}{ntnu.no}}}%
\hspace*{\stretch{1}}%
%% uncomment if additional authors present
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering E. Torre\\%
\footnotesize\epost{\email{emiliano.torre}{yahoo.com}}}%
\hspace*{\stretch{1}}\\%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering V. Rostami\\%
\footnotesize\epost{\email{vrostami}{uni-koeln.de}}}%
\hspace*{\stretch{1}}%
\parbox{0.5\linewidth}%\makebox[0pt][c]%
{\protect\centering Y. Roudi\\%
\footnotesize\epost{\email{yasser.roudi}{ntnu.no}}}%
\hspace*{\stretch{1}}%
%\quad\href{https://orcid.org/0000-0002-6070-0784}{\protect\includegraphics[scale=0.16]{orcid_32x32.png}\textsc{orcid}:0000-0002-6070-0784}%
}

@@

The question of how large the larger population addressed by model should
or can be, and the assumptions on which the model is based, from a Bayesian
point of view, are also discussed.
% \\\noindent\emph{\footnotesize Note:
%   Dear Reader \amp\ Peer, this manuscript is being peer-reviewed by you.
%   Thank you.}
% \par%\\[\jot]
% \noindent
% {\footnotesize PACS: ***}\qquad%
% {\footnotesize MSC: ***}%
%\qquad{\footnotesize Keywords: ***}
\end{abstract}
\selectlanguage{british}\frenchspacing

@@

The two infinity approximations are at the edge of their validity range, in
our examples. For this reason we interpret the maximum-entropy distribution
as \emph{the most probable frequency distributions}, as mentioned at the
end of \sect~\ref{sec:model}. In high dimensions, however, the features of
the most plausible distribution may not be \emph{typical} of the majority
of plausible distributions. An important question, then, is \emph{which
  features of the maximum-entropy frequency distribution are typical of the
  majority of plausible frequency distributions?} -- especially for
features such as the number, position, and heights of modes; or tail
behaviour. Preliminary studies using a full probability calculation (in
preparation, to be published separately) indicate that several
semi-quantitative features of the maximum-entropy distribution are indeed
typical. For the first data set, for example, most frequency distributions
have a high-frequency regime at a population-averaged activity of around
0.075, as in \fig~\ref{fig:plots_5mom_a}, but their second high-frequency
regime is typically lower and appears for $N>5\,000$. Most frequency
distributions have two or three very close modes within each high-frequency
regime, rather than one. The same preliminary studies also indicate that
these typical features are insensitive to alternative prior choices in the
second assumption above, for example using a Dirichlet prior instead of an
entropic one.

@@

Some approximations implicit in the model make its numerical results
semi-quantitative with respect to an exact analysis.%  The results should not
% be off by more than a few percentages for the population-averaged
% activity and for the frequency density.
This imprecision, however, is compensated by the
extreme computational cheapness of the model, far less costly than an exact
analysis. The model is therefore very convenient at least for essaying
hypotheses. We hope to present an exact quantitative comparison with the
full probabilistic approach in a future publication.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% Bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\clearpage
\defbibnote{prenote}{{\footnotesize (\enquote{de $X$} is listed under D,
    \enquote{van $X$} under V, and so on, regardless of national
    conventions.)\par}}
% \defbibnote{postnote}{\par\medskip\noindent{\footnotesize% Note:
%     \arxivp \mparcp \philscip \biorxivp}}
